SI: Settlements / Neo

### 2022-06-23 analysis/neo/neo.Rmd
add separate reports for various time resolutions
analysis for Neolithic B and C

```{r pca-plot}
pca_per %>% plot_nested_pca(var = "period")
```

>>>>

```{r pca-plot}
pca_per %>% 
  mutate(reg = if_else(reg == "B", "East Bohemia", "Morava river catchment")) %>% 
  plot_nested_pca(var = "period")
```

```{r}
# ggsave(here::here("neo_pca.svg"), width = 10, height = 7)
```

```{r pca-summations}
loadings_sum <- pca_per %>% 
  summarise_variables()
```

```{r pca-summations-tb}
loadings_sum %>% 
  mutate(r = (PC1 + PC2 + PC3 + PC4 + PC5)/(ncol(loadings_sum) - 1)) %>% 
  select(column, r) %>% 
  arrange(reg, desc(r)) %>% 
  knitr::kable()
```

```{r}
# loadings_sum %>% 
#   mutate(r = (PC1 + PC2 + PC3 + PC4 + PC5)/(ncol(loadings_sum) - 1)) %>% 
#   select(column, r) %>% 
#   arrange(reg, desc(r)) %>% 
#   write_csv(here::here("neo_faktory.csv"))
```
